---
title: "Facebook Advertisement Image Analysis"
author: "Samantha Chiu and Leanna Moron"
date: "31 OCT"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

Data sources are week 1-2 Facebook Advertisement Image data with fieldwork dates are from 14 May to 28 May (for all 5 Advertisement Images, no social desirability questions or image changes were introduced in these weeks). UAS 244 data is used with fieldwork dates of 5/13-6/9.  

# Summary of Data

```{r, loading FB data, include = FALSE}
library(tidyverse)
library(haven)
library(knitr)
library(expss)
library(tinytex)
week12 <- read_dta("C:/Users/Samantha/Desktop/week12.dta")
#View(week12)
attach(week12)
```

Confirming the four respondents who are ineligible (under 18 years old) have been removed

``` {r, examining age eligibility, include = FALSE}
#summary (Q11)
table (Q11)
```

``` {r, removing under 18, echo = FALSE}
data <- subset(week12, Q11 >= 2)
cro(data$Q11)
```

```{r, loading UAS data, include = FALSE}
# Looking at age ranges for UAS survey (table supressed -- regrouping needed)
uas244 <- read_dta("C:/Users/Samantha/Desktop/uas244.dta")
#cro(uas244$agerange)
```

Total sample from each advertisement image

```{r, echo = FALSE}
cro(data$Image)
```
## Comparing by Advertisement Images by Question

The following section are the comparison tables for the 5 advertisement images

### Mental Health
```{r, echo = FALSE, include = FALSE}
cro(data$Q1)
```

```{r, raw data, include = FALSE}
table_Q1 <- table(data$Q1, data$Image)
print(table_Q1)
prop.table(table_Q1, 2)
chisq.test((table_Q1))
```

```{r, totals for Kable, include = FALSE}
totals <- addmargins(table(data$Q1, data$Image))
totals
total <- c(343, 576, 61, 145, 210)
```

```{r, setting up table for Kable, include = FALSE}
library(kableExtra)
library(dplyr)
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q1, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Not at all", "Several Days", "More Then Half The Days", "Nearly Every Day", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```

```{r, kable table, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 1. Responses from five advertisement image samples for \"In the past fourteen days, how often have you felt nervous, anxious, or on edge?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 65.182, df = 12, p < 0.001", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, echo = FALSE, include = FALSE}
cro(data$Q2)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q2, data$Image))
totals
total <- c(343, 575, 61, 145, 210)
```

```{r, include = FALSE}
table_Q2 <- table(data$Q2, data$Image)
prop.table(table_Q2,2)
print(table_Q2)
chisq.test((table_Q2))
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q2, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Not At All or Less Than 1 Day", "1-2 Days", "3-4 Days", "5-7 Days", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 2. Responses from five advertisement image samples for \"In the past 7 days, how often have you felt depressed?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 35.237, df = 12, p < 0.001", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

### Data Privacy
```{r, include = FALSE}
cro(data$Q3)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q3, data$Image))
totals
total <- c(174, 289, 29, 71, 105)
```

```{r, include = FALSE}
table_Q3 <- table(data$Q3, data$Image)
prop.table(table_Q3,2)
print(table_Q3)
chisq.test((table_Q3))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q3, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 3. Responses from five advertisement image samples for \"Sensors installed on a smartphone collect data on  health conditions. With consent of the owner, these data are transmitted to a public authority for the purpose of detecting outbreaks of diseases early and for developing solutions. The data are safe, anonymous, and protected from misuse. How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 21.669, df = 16, p = 0.1542", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q3_1)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q3_1, data$Image))
totals
total <- c(169, 285, 32, 104, 663)
```

```{r, include = FALSE}
table_Q3_1 <- table(data$Q3_1, data$Image)
prop.table(table_Q3_1,2)
print(table_Q3)
chisq.test((table_Q3_1))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q3_1, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 3_1. Responses from five advertisement image samples for \"Sensors installed on a smartphone collect data on  health conditions. With consent of the owner, these data are transmitted to a public authority for the purpose of detecting outbreaks of diseases early and for developing solutions. How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 37.79, df = 16, p = 0.0016", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q4)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q4, data$Image))
totals
total <- c(343, 575, 61, 144, 210)
```

```{r, include = FALSE}
table_Q4 <- table(data$Q4, data$Image)
prop.table(table_Q4,2)
print(table_Q4)
chisq.test((table_Q4))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q4, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 4. Responses from five advertisement image samples for \"Smartphones with navigation apps collect location data on mobility. With consent of the owner, these data are transmitted to a public authority. The public authority uses these data to measure social distancing in communities. The data are safe, anonymous, and protected from misuse. How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 56.29, df = 16, p < 0.001", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

### COVID-19
```{r, include = FALSE}
cro(data$Q5)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q5, data$Image))
totals
total <- c(342, 577, 61, 145, 210)
```

```{r, include = FALSE}
table_Q5 <- table(data$Q5, data$Image)
prop.table(table_Q5,2)
print(table_Q5)
chisq.test((table_Q5))
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q5, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Very Unlikely", "Somewhat Unlikely", "Somewhat Likely", "Very Likely", "Unsure", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 5. Responses from five advertisement image samples for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 70.07 (approximation may be incorrect due to low cell count), df = 16, p < 0.001", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q6)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q6, data$Image))
totals
total <- c(342, 577, 61, 145, 210)
```

```{r, include = FALSE}
table_Q6 <- table(data$Q6, data$Image)
prop.table(table_Q6,2)
print(table_Q6)
chisq.test((table_Q6))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q6, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 6. Responses from five advertisement image samples for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 11.06, df = 8, p = 0.1983", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```


# Finance

```{r}
# Variable (Q7) requires recoding into groups: discuss the group breaks
```

```{r, include = FALSE}
cro(data$Q8)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q8, data$Image))
totals
total <- c(342, 573, 61, 144, 209)
```

```{r, include = FALSE}
table_Q8 <- table(data$Q8, data$Image)
prop.table(table_Q8,2)
print(table_Q8)
chisq.test((table_Q8))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q8, 2)*100, format = "f", digits =2), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("Control", "COVID", "Data Privacy","Finance", "Mental Health")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 8. Responses from five advertisement image samples for \"In the past seven days, were you worried you would run out of food because of a lack of money or other resources?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 9.14, df = 8, p = 0.3303", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

### Gender identity
```{r, echo = FALSE}
cro(data$Q9)
```

```{r, echo = FALSE}
table_Q9 <- table(data$Q9, data$Image)
prop.table(table_Q9,2)
print(table_Q9)
chisq.test((table_Q9))
# Response Options 
# 1 = Woman, 2 = Man, 3 = Trans woman, 4 = Trans man, 5 = Non-binary 6 = Other
```

### Married
```{r, echo = FALSE}
cro(data$Q10)
```

```{r, echo = FALSE}
table_Q10 <- table(data$Q10, data$Image)
prop.table(table_Q10,2)
print(table_Q10)
chisq.test((table_Q10))
```

### Age
```{r, echo = FALSE}
cro(data$Q11)
```

```{r, echo = FALSE}
table_Q11 <- table(data$Q11, data$Image)
prop.table(table_Q11,2)
print(table_Q11)
chisq.test((table_Q11))
## discuss
```

### Education 
```{r, echo = FALSE}
cro(data$Q12)
```

```{r, echo = FALSE}
table_Q12 <- table(data$Q12, data$Image)
prop.table(table_Q12,2)
print(table_Q12)
chisq.test((table_Q12))
```

## UAS Sample
```{r, echo = FALSE}
#colnames(uas244)
attach(uas244)

# To do: clean out dates that do not overlap (10-18)
#table (start_month, start_date)
library(tidyverse)
```

# Question 1: Mental Health
```{r, echo = FALSE}
cro(uas244$cr027a)
```

# Question 2: Mental Health  
```{r, echo = FALSE}
cro(uas244$cr027c)
```

# Question 5: COVID-19
```{r, echo = FALSE}
cro(uas244$cr030)
```

# Question 6: COVID-19
```{r, echo = FALSE}
cro(uas244$cr018a)
```

# Question 7: Finance
```{r, echo = FALSE}
# Recode into groups
# cro(uas244$lr015)
```

# Question 8: Finance 
```{r, echo = FALSE}
cro(uas244$ei002)
```
# Question 9: Gender
```{r, echo = FALSE}
cro(uas244$gender)
```

# Question 10: Marital Status
```{r, echo = FALSE}
cro(uas244$maritalstatus)
```

# Question 11: Age Range
```{r, echo = FALSE}
cro(uas244$agerange)
```
# Question 12: Education
```{r, echo = FALSE}
cro(uas244$education)
```

## POOLED AD IMAGES WITH UAS WEIGHTS 

### MENTAL HEALTH

```{r, include = FALSE}
library(survey)
#colnames(uas244)
attach(uas244)
design <- svydesign(id=~1, weights=final_weight, data=uas244)

table_cr027a_w <-svytable(~cr027a, design = design)
table_Q1 <-table(data$Q1)
table_MH_1_w <- cbind(table_cr027a_w, table_Q1)
table_MH_1_w

totals <- addmargins(table_Q1)
totals
totals <- addmargins(table_cr027a_w)
totals
totals <- c(627.56, 1335)

prop.table(table_MH_1_w, 2)
chisq.test(table_MH_1_w)
```

```{r, echo = FALSE, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_MH_1_w, 2)*100, format = "f", digits =2), formatC(totals, format ="d"))
rownames(table) <- c("Not At All or Less Than 1 Day", "1-2 Days", "3-4 Days", "5-7 Days", "Total N")
colnames(table) <- c("UAS Sample", "Facebook Ad Image Sample")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 1. Responses from Understanding Americas Survey and Facebook Advertisement Image Pooled Samples for \"In the past fourteen days, how often have you felt nervous, anxious, or on edge?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 305.6, df = 3, p < 0.001", notation = "none") %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

# Question 2: In the past 7 days, how often have you felt depressed?
# UAS and Pooled Ad Images

```{r}
table_cr027c_w <- svytable(~cr027c, design = design)
table_Q2 <-table (data$Q2)
table_MH_2_w <- cbind(table_cr027c_w, table_Q2)
prop.table(table_MH_2_w, 2)
chisq.test(table_MH_2_w)
```
# Question 3: Data Privacy
# Texas Survey (TBD)

# Question 3_1: Data Privacy
# Texas Survey (TBD)

# Question 4: Data Privacy
# Texas Survey (TBD)

# Question 5: COVID19 -- vaccinated if available? 
```{r}
table_cr030_w <- svytable(~cr030, design = design)
table_Q5 <-table (data$Q5)
table_COVID_1_w <- cbind(table_cr030_w, table_Q5)
prop.table(table_COVID_1_w, 2)
chisq.test(table_COVID_1_w)
```

# Question 6: COVID 19 -- limiting non essential travel 
```{r}
table_cr018a_w <- svytable(~cr018a, design = design)
table_Q6 <-table (data$Q6)
table_COVID_2_w <- cbind(table_cr018a_w, table_Q6)
prop.table(table_COVID_2_w, 2)
chisq.test(table_COVID_2_w)
```
# Question 7: Finance -- run out of money (recode needed)

# Question 8: Finance -- run out of food
```{r}
table_ei002_w <- svytable(~ei002, design = design)
table_Q8 <-table (data$Q8)
table_FINANCE_2_w <- cbind(table_ei002_w, table_Q8)
prop.table(table_FINANCE_2_w, 2)
chisq.test(table_FINANCE_2_w)
```
## Looking at Control Data Only
```{r}
control.data <- subset(data, data$Image == 1)
cro(control.data$Image)
```
# Question 1: Mental Health 
# UAS weighted and Control Image Only

```{r}
library(DescTools)

table_Q1_control <-table(control.data$Q1)
prop.table(table_Q1_control)

table_MH_1_w_control<- cbind(table_cr027a_w, table_Q1_control)
print(table_MH_1_w_control)
prop.table(table_MH_1_w_control, 2)
chisq.test(table_MH_1_w_control)
```
```{r}
Desc(table_MH_1_w_control, verbose = "high")
```

# Question 2: How often have you felt depressed
# UAS weighted and control image only

```{r}
table_Q2_control <-table(control.data$Q2)
prop.table(table_Q2_control)

table_MH_2_w_control<- cbind(table_cr027a_w, table_Q2_control)
print(table_MH_2_w_control)
prop.table(table_MH_2_w_control, 2)
chisq.test(table_MH_2_w_control)
```
```{r}
Desc(table_MH_2_w_control, verbose = "high")
```

# Question 5: COVID - vaccine
# UAS weighted and control image only

```{r}
table_Q5_control <-table(control.data$Q5)
prop.table(table_Q5_control)

table_COVID_1_w_control<- cbind(table_cr030_w, table_Q5_control)
print(table_COVID_1_w_control)
prop.table(table_COVID_1_w_control, 2)
chisq.test(table_COVID_1_w_control)
```
# Question 6: COVID - limit travel
# UAS weighted and control image only

```{r}
table_Q6_control <-table(control.data$Q6)
prop.table(table_Q6_control)

table_COVID_2_w_control<- cbind(table_cr018a_w, table_Q6_control)
print(table_COVID_2_w_control)
prop.table(table_COVID_2_w_control, 2)
chisq.test(table_COVID_2_w_control)
```

# Question 8: Finance - run out of food
# UAS weighted and control image only

```{r}
table_Q8_control <-table(control.data$Q8)
prop.table(table_Q8_control)

table_FINANCE_2_w_control<- cbind(table_ei002_w, table_Q8_control)
print(table_FINANCE_2_w_control)
prop.table(table_FINANCE_2_w_control, 2)
chisq.test(table_FINANCE_2_w_control)
```

# UAS weighted, control image, pooled (witout control)

```{r}
pooled.data <- subset(data, data$Image > 1)
cro(pooled.data$Image)
```

```{r}
table_pooled_Q1 <-table(pooled.data$Q1)
table_Q1_pcw <- cbind(table_Q1, table_pooled_Q1, table_cr027a_w)
print(table_Q1_pcw)
prop.table(table_Q1_pcw, 2)
chisq.test(table_Q1_pcw)
```
```{r}
summary(table_Q1)
summary(table_pooled_Q1)
test<-table(cr027a)
summary(test)
```
```{r}
total <- c(1335, 992, 6311)
```

```{r}
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q1_pcw, 2), format = "f" , digits = 2), formatC(total, format = "d"))
rownames(table) <- c("Not at all", "Several Days", "More Then Half The Days", "Nearly Every Day", "Total N")
colnames(table) <- c("Control Image", "All Other Images", "UAS Only")
table
```

```{r}
require(knitr)

kable(table, 
            caption = "Table 1. Comparing Control Image, All Other Images, and UAS Only Sample for \"In the past fourteen days, how often have you felt nervous, anxious, or on       edge?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote("Note: Proportion of respondents for each category; X-squared = 508.7, df = 6, p = 2.2e-16", notation = "none") %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```



```{r}
table_pooled_Q2 <-table(pooled.data$Q2)
table_Q2_pcw <- cbind(table_Q2, table_pooled_Q2, table_cr027c_w)
print(table_Q2_pcw)
prop.table(table_Q2_pcw, 2)
chisq.test(table_Q2_pcw)
```

```{r}
table_pooled_Q5 <-table(pooled.data$Q5)
table_Q5_pcw <- cbind(table_Q5, table_pooled_Q5, table_cr030_w)
print(table_Q5_pcw)
prop.table(table_Q5_pcw, 2)
chisq.test(table_Q5_pcw)
```

```{r}
table_pooled_Q6 <-table(pooled.data$Q6)
table_Q6_pcw <- cbind(table_Q6, table_pooled_Q6, table_cr018a_w)
print(table_Q6_pcw)
prop.table(table_Q6_pcw, 2)
chisq.test(table_Q6_pcw)
```

```{r}
table_pooled_Q8 <-table(pooled.data$Q8)
table_Q8_pcw <- cbind(table_Q8, table_pooled_Q8, table_ei002_w)
print(table_Q8_pcw)
prop.table(table_Q8_pcw, 2)
chisq.test(table_Q8_pcw)
```

# control image, pooled (witout control)

```{r}
table_Q1_pc <- cbind(table_Q1, table_pooled_Q1)
print(table_Q1_pc)
prop.table(table_Q1_pc, 2)
chisq.test(table_Q1_pc)
```
```{r}
table_Q2_pc <- cbind(table_Q2, table_pooled_Q2)
print(table_Q2_pc)
prop.table(table_Q2_pc, 2)
chisq.test(table_Q2_pc)
```
```{r}
table_Q5_pc <- cbind(table_Q5, table_pooled_Q5)
print(table_Q5_pc)
prop.table(table_Q5_pc, 2)
chisq.test(table_Q5_pc)
```

```{r}
table_Q6_pc <- cbind(table_Q6, table_pooled_Q6)
print(table_Q6_pc)
prop.table(table_Q6_pc, 2)
chisq.test(table_Q6_pc)
```

```{r}
table_Q8_pc <- cbind(table_Q8, table_pooled_Q8)
print(table_Q8_pc)
prop.table(table_Q8_pc, 2)
chisq.test(table_Q8_pc)
```

```{r}
cro(uas244$education)
```

