---
title: "Facebook Advertisement Image Analysis"
author: "Samantha Chiu and Leanna Moron"
date: "26 NOV"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

Data sources are weeks 1-2 of the Facebook advertisement image data fielded from 5/14/20-5/28/20, and Understanding America Survey (UAS-255, wave 5) fielded from 5/13/20 to 6/9/20. The five (5) advertisement images include a neutral image, COVID, data privacy, finance and mental health. There were no social desirability questions fielded during this time period. The data privacy and finance ad images did not change during this time period.

```{r, loading FB data, include = FALSE}
library(tidyverse)
library(haven)
library(knitr)
library(expss)
library(tinytex)
library(kableExtra)
library(dplyr)

week12 <- read_dta("C:/Users/Samantha/Desktop/week12.dta")
#View(week12)
attach(week12)
```

``` {r, examining age eligibility, include = FALSE}
#summary (Q11)
table (Q11)
```

``` {r, removing under 18, echo = FALSE, include = FALSE}
data <- subset(week12, Q11 >= 2)
cro(data$Q11)
```

```{r, loading UAS data, include = FALSE}
# Looking at age ranges for UAS survey (table supressed -- regrouping needed)
uas244 <- read_dta("C:/Users/Samantha/Desktop/uas244.dta")
#cro(uas244$agerange)
```

```{r, echo = FALSE, include = FALSE}
cro(data$Image)
```
## Comparing by Advertisement Images by Question

The following section are the comparison tables for the 5 advertisement images using the Facebook Advertisent Image data 

### Mental Health
```{r, echo = FALSE, include = FALSE}
cro(data$Q1)
```

```{r, raw data, include = FALSE}
table_Q1 <- table(data$Q1, data$Image)
print(table_Q1)
prop.table(table_Q1, 2)
chisq.test((table_Q1))
```

```{r, totals for Kable, include = FALSE}
totals <- addmargins(table(data$Q1, data$Image))
totals
total <- c(343, 576, 61, 145, 210)
```

```{r, setting up table for Kable, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q1, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Not at all", "Several Days", "More Then Half The Days", "Nearly Every Day", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```

```{r, kable table, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 1. Responses from five advertisement image samples for \"In the past fourteen days, how often have you felt nervous, anxious, or on edge?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 65.182, df = 12, p < 0.001", notation = "none") %>%
row_spec(5, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, echo = FALSE, include = FALSE}
cro(data$Q2)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q2, data$Image))
totals
total <- c(343, 575, 61, 145, 210)
```

```{r, include = FALSE}
table_Q2 <- table(data$Q2, data$Image)
prop.table(table_Q2,2)
print(table_Q2)
chisq.test((table_Q2))
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q2, 2)*100, format = "f", digits =1), formatC(total, format ="d"))
rownames(table) <- c("Not At All or Less Than 1 Day", "1-2 Days", "3-4 Days", "5-7 Days", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 2. Responses from five advertisement image samples for \"In the past 7 days, how often have you felt depressed?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 35.237, df = 12, p < 0.001", notation = "none") %>%
row_spec(5, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

### Data Privacy
```{r, include = FALSE}
cro(data$Q3)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q3, data$Image))
totals
total <- c(174, 289, 29, 71, 105)
```

```{r, include = FALSE}
table_Q3 <- table(data$Q3, data$Image)
prop.table(table_Q3,2)
print(table_Q3)
chisq.test((table_Q3))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q3, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 3. Responses from five advertisement image samples for \"Sensors installed on a smartphone collect data on  health conditions. With consent of the owner, these data are transmitted to a public authority for the purpose of detecting outbreaks of diseases early and for developing solutions. **The data are safe, anonymous, and protected from misuse.** How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 21.669, df = 16, p = 0.1542", notation = "none") %>%
row_spec(6, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q3_1)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q3_1, data$Image))
totals
total <- c(169, 285, 32, 104, 663)
```

```{r, include = FALSE}
table_Q3_1 <- table(data$Q3_1, data$Image)
prop.table(table_Q3_1,2)
print(table_Q3)
chisq.test((table_Q3_1))
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q3_1, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 3_1. Responses from five advertisement image samples for \"Sensors installed on a smartphone collect data on  health conditions. With consent of the owner, these data are transmitted to a public authority for the purpose of detecting outbreaks of diseases early and for developing solutions. How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 37.79, df = 16, p = 0.0016", notation = "none") %>%
row_spec(6, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q4)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q4, data$Image))
totals
total <- c(343, 575, 61, 144, 210)
```

```{r, include = FALSE}
table_Q4 <- table(data$Q4, data$Image)
prop.table(table_Q4,2)
print(table_Q4)
chisq.test((table_Q4))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q4, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Not Acceptable", "Barely Acceptable", "Medium Acceptable", "Quite Acceptable", "Very Acceptable", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 4. Responses from five advertisement image samples for \"Smartphones with navigation apps collect location data on mobility. With consent of the owner, these data are transmitted to a public authority. The public authority uses these data to measure social distancing in communities. The data are safe, anonymous, and protected from misuse. How acceptable is it to you to use these data for this purpose?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 56.29, df = 16, p < 0.001", notation = "none") %>%
row_spec(6, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

### COVID-19
```{r, include = FALSE}
cro(data$Q5)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q5, data$Image))
totals
total <- c(342, 577, 61, 145, 210)
```

```{r, include = FALSE}
table_Q5 <- table(data$Q5, data$Image)
prop.table(table_Q5,2)
print(table_Q5)
chisq.test((table_Q5))
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q5, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Very Unlikely", "Somewhat Unlikely", "Somewhat Likely", "Very Likely", "Unsure", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 5. Responses from five advertisement image samples for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 70.07 (approximation may be incorrect due to low cell count), df = 16, p < 0.001", notation = "none") %>%
row_spec(6, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, include = FALSE}
cro(data$Q6)
```

```{r, include = FALSE}
totals <- addmargins(table(data$Q6, data$Image))
totals
total <- c(342, 577, 61, 145, 210)
```

```{r, include = FALSE}
table_Q6 <- table(data$Q6, data$Image)
prop.table(table_Q6,2)
print(table_Q6)
chisq.test((table_Q6))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q6, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 6. Responses from five advertisement image samples for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 11.06, df = 8, p = 0.1983", notation = "none") %>%
row_spec(4, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```


### Finance

```{r}
# Variable (Q7) requires recoding into groups: discuss the group breaks
```

```{r, include = FALSE}
cro(data$Q8)
```
```{r, include = FALSE}
totals <- addmargins(table(data$Q8, data$Image))
totals
total <- c(342, 573, 61, 144, 209)
```

```{r, include = FALSE}
table_Q8 <- table(data$Q8, data$Image)
prop.table(table_Q8,2)
print(table_Q8)
chisq.test((table_Q8))
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_Q8, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("Neutral (%)", "COVID (%)", "Data Privacy (%)","Finance (%)", "Mental Health (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 8. Responses from five advertisement image samples for \"In the past seven days, were you worried you would run out of food because of a lack of money or other resources?\"", 
      digits = 2, 
      align = "c") %>%
add_footnote ("Note: Proportion of respondents by image for each response category; X-squared = 9.14, df = 8, p = 0.3303", notation = "none") %>%
row_spec(4, bold = TRUE) %>%
kable_styling (latex_options = c("striped", full_width = F, "hold_position"))
```

## UAS SAMPLE (Weighted) with Facebook Ad Image (All) 

Comparing the USC Understanding America Sample (weighted) and Facebook Advertisement Image (pooled all 5 images) data  

### MENTAL HEALTH

```{r, include = FALSE}
library(survey)
#colnames(uas244)
attach(uas244)
```


```{r, include = FALSE}
design <- svydesign(id=~1, weights=final_weight, data=uas244)
table_cr027a_w <-svytable(~cr027a, design = design)
table_Q1 <-table(data$Q1)
table_MH_1_w <- cbind(table_cr027a_w, table_Q1)
table_MH_1_w

totals <- addmargins(table_Q1)
totals
totals <- addmargins(table_cr027a_w)
totals
totals <- c(6287.56, 1335)

prop.table(table_MH_1_w, 2)
chisq.test(table_MH_1_w)
```

```{r, echo = FALSE, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_MH_1_w, 2)*100, format = "f", digits = 1), formatC(totals, format ="d"))
rownames(table) <- c("Not At All or Less Than 1 Day", "1-2 Days", "3-4 Days", "5-7 Days", "Total N")
colnames(table) <- c("UAS Sample (%)", "Facebook Ad Image Sample (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 1. Responses from Understanding America Survey and Facebook Advertisement Image Sample for \"In the past fourteen days, how often have you felt nervous, anxious, or on edge?\"", 
      digits = 2, 
      align = "c") %>% 
  add_footnote ("Note: Proportion of UAS and FB respondents for each response category; X-squared = 305.6, df = 3, p < 0.001", notation = "none") %>%
  row_spec(5, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, echo=FALSE, include=FALSE}
table_cr027c_w <- svytable(~cr027c, design = design)
table_Q2 <-table (data$Q2)
table_MH_2_w <- cbind(table_cr027c_w, table_Q2)

total.uas<-addmargins(table_cr027c_w)
total.uas
total.uas[[length(total.uas)]]

total.fb<-addmargins(table_Q2)
total.fb
total.fb[[length(total.fb)]]

total<-cbind(total.uas[[length(total.uas)]], total.fb[[length(total.fb)]])
total

prop.table(table_MH_2_w, 2)
chisq.test(table_MH_2_w)
```
```{r, echo = FALSE, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_MH_2_w, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Not At All or Less Than 1 Day", "1-2 Days", "3-4 Days", "5-7 Days", "Total N")
colnames(table) <- c("UAS Sample (%)", "Facebook Ad Image Sample (%)")
table
```
```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 2. Responses from Understanding America Survey and Facebook Advertisement Image Sample for \"In the past 7 days, how often have you felt depressed? \"", 
      digits = 2, 
      align = "c") %>% 
  add_footnote ("Note: Proportion of UAS and FB respondents for each response category; X-squared = 272.9, df = 3, p < 0.001", notation = "none") %>%
  row_spec(5, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

### Data Privacy

Questions (Q3, Q3_1, Q4) on data privacy were not fielded in the UAS study; therefore, they are not included in the UAS to FB sample comparison

### COVID-19 
```{r, echo=FALSE, include=FALSE}
table_cr030_w <- svytable(~cr030, design = design)
table_Q5 <-table (data$Q5)
table_COVID_1_w <- cbind(table_cr030_w, table_Q5)
prop.table(table_COVID_1_w, 2)
chisq.test(table_COVID_1_w)

total.uas<-addmargins(table_cr030_w)
total.uas
total.fb<-addmargins(table_Q5)
total.fb
total<-cbind(total.uas[[length(total.uas)]],total.fb[[length(total.fb)]])
```

```{r, echo=FALSE, include=FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_COVID_1_w, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Very Unlikely", "Somewhat Unlikely", "Somewhat Likely", "Very Likely", "Unsure" ,"Total N")
colnames(table) <- c("UAS Sample (%)", "Facebook Ad Image Sample (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 1. Responses from Understanding America Survey and Facebook Advertisement Image Sample for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
      digits = 2, 
      align = "c") %>% 
  add_footnote ("Note: Proportion of UAS and FB respondents for each response category; X-squared = 276.6, df = 4, p < 0.001", notation = "none") %>%
  row_spec(6, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

```{r, echo=FALSE, include=FALSE}
table_cr018a_w <- svytable(~cr018a, design = design)
table_Q6 <-table (data$Q6)
table_COVID_2_w <- cbind(table_cr018a_w, table_Q6)
prop.table(table_COVID_2_w, 2)
chisq.test(table_COVID_2_w)

total.uas<-addmargins(table_cr018a_w)
total.uas[[length(total.uas)]]
total.fb<-addmargins(table_Q6)
total.fb[[length(total.fb)]]
total<-cbind(total.uas[[length(total.uas)]], total.fb[[length(total.fb)]])

```

```{r, echo=FALSE, include=FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_COVID_2_w, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("UAS Sample (%)", "Facebook Ad Image Sample (%)")
table
```

```{r, echo = FALSE}
require(knitr)
kable(table, 
      caption = "Table 6. Responses from Understanding Americas Survey and Facebook Advertisement Image Sample for \"Are Federal, state, or local governments currently requiring you to limit non-essential travel?\"", 
      digits = 2, 
      align = "c") %>% 
  add_footnote ("Note: Proportion of UAS and FB respondents for each response category; X-squared = 64.3, df = 2, p < 0.001", notation = "none") %>%
  row_spec(4, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

### FINANCE

Table 7. The first finance question is on a 0-100 scale. 

```{r, echo=FALSE, include=FALSE}
#table_lr015_w <- svytable(~lr015, design = design)
#table_Q8 <-table (data$Q8)
#table_FINANCE_1_w <- cbind(table_lr015_w, table_Q7) #need to create table_Q7
#prop.table(table_FINANCE_1_w, 2)
#chisq.test(table_FINANCE_1_w)
```


```{r, echo=FALSE, include=FALSE}
table_ei002_w <- svytable(~ei002, design = design)
table_Q8 <-table (data$Q8)
table_FINANCE_2_w <- cbind(table_ei002_w, table_Q8)
prop.table(table_FINANCE_2_w, 2)
chisq.test(table_FINANCE_2_w)

total.uas<-addmargins(table_ei002_w)
total.uas[[length(total.uas)]]
total.fb<-addmargins(table_Q8)
total.fb[[length(total.fb)]]
total<-cbind(total.uas[[length(total.uas)]], total.fb[[length(total.fb)]])
```

```{r, echo = FALSE, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table <- rbind(formatC(prop.table(table_FINANCE_2_w, 2)*100, format = "f", digits = 1), formatC(total, format ="d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("UAS Sample (%)", "Facebook Ad Image Sample (%)")
table
```

```{r, echo=FALSE}
kable(table, 
      caption = "Table 8. Responses from Understanding Americas Survey and Facebook Advertisement Image Sample for \"In the past seven days, were you worried you would run out of food because of a lack of money or other resources?\"", 
      digits = 2, 
      align = "c") %>% 
  add_footnote ("Note: Proportion of UAS and FB respondents for each response category; X-squared = 13.0, df = 2, p < 0.01", notation = "none") %>%
  row_spec(4, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

## UAS weighted, pooled (without control), control image

```{r, include = FALSE}
pooled.data <- subset(data, data$Image > 1)
cro(pooled.data$Image)
table_pooled_Q1 <-table(pooled.data$Q1)
table_pooled_Q1
prop.table(table_pooled_Q1)
```

```{r, include = FALSE}
control.data <- subset(data, data$Image == 1)
cro(control.data$Image)
cro(control.data$Q1)
table_Q1_control <-table(control.data$Q1)
table_Q1_control
prop.table(table_Q1_control)
```


```{r, include = FALSE}
table_Q1_pcw <- cbind(table_cr027a_w, table_pooled_Q1, table_Q1_control)
print(table_Q1_pcw)
prop.table(table_Q1_pcw, 2)
chisq.test(table_Q1_pcw)
```

```{r, include = FALSE}
total.uas<-addmargins(table_cr027a_w)
total.uas[[length(total.uas)]]

total.control<-addmargins(table_Q1_control)
total.control[[length(total.control)]]

total.pooled<-addmargins(table_pooled_Q1)
total.pooled[[length(total.pooled)]]

total<-cbind(total.uas[[length(total.uas)]], total.pooled[[length(total.pooled)]], total.control[[length(total.control)]])
total
```

```{r, include = FALSE}
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q1_pcw, 2)*100, format = "f" , digits = 1), formatC(total, format = "d"))
rownames(table) <- c("Not at all", "Several Days", "More Then Half The Days", "Nearly Every Day", "Total N")
colnames(table) <- c("UAS Only (%)", "All Other Images (%)",  "Neutral Image (%)")
table
```

```{r, echo = FALSE}
require(knitr)

kable(table, 
            caption = "Table 1. Comparing responses from Understanding America Survey, Facebook Advertisement Image, and Control Image Only for \"In the past fourteen days, how often have you felt nervous, anxious, or on edge?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote("Note: X$^{2}$ = 371.3, 6 df, p < 0.001", notation = "none") %>%
  row_spec(5, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```
```{r, include = FALSE}
cro(pooled.data$Image)
table_pooled_Q2 <-table(pooled.data$Q2)
table_pooled_Q2
prop.table(table_pooled_Q2)
```
```{r, include = FALSE}
table_Q2_control <-table(control.data$Q2)
table_Q2_control
prop.table(table_Q2_control)
```
```{r, include = FALSE}
table_Q2_pcw <- cbind(table_cr027c_w, table_pooled_Q2, table_Q2_control)
print(table_Q2_pcw)
prop.table(table_Q2_pcw, 2)
chisq.test(table_Q2_pcw)
```

```{r, include = FALSE}
total.uas<-addmargins(table_cr027c_w)
total.uas[[length(total.uas)]]

total.control<-addmargins(table_Q2_control)
total.control[[length(total.control)]]

total.pooled<-addmargins(table_pooled_Q2)
total.pooled[[length(total.pooled)]]

total<-cbind(total.uas[[length(total.uas)]], total.pooled[[length(total.pooled)]], total.control[[length(total.control)]])
total
```

```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q2_pcw, 2)*100, format = "f" , digits = 1), formatC(total, format = "d"))
rownames(table) <- c("Not at all", "Several Days", "More Then Half The Days", "Nearly Every Day", "Total N")
colnames(table) <- c("UAS Only (%)", "All Other Images (%)",  "Neutral Image (%)")
table
```

```{r, echo = FALSE}
require(knitr)

kable(table, 
            caption = "Table 2. Comparing responses from Understanding America Survey, Facebook Advertisement Pooled Images, and Control Image Only for \"In the past 7 days, how often have you felt depressed?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote(" X$^{2}$ = 298.1, 6 df, p < 0.001", notation = "none") %>%
  row_spec(5, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```
### Data Privacy
Questions (Q3, Q3_1, Q4) on data privacy were not fielded in the UAS study; therefore, they are not included in the UAS to FB sample comparison

### COVID-19

```{r, include = FALSE}
table_pooled_Q5 <-table(pooled.data$Q5)
table_pooled_Q5
prop.table(table_pooled_Q5)
```
```{r, include = FALSE}
table_Q5_control <-table(control.data$Q5)
table_Q5_control
prop.table(table_Q5_control)
```
```{r, include = FALSE}
total.uas<-addmargins(table_cr030_w)
total.uas[[length(total.uas)]]

total.control<-addmargins(table_Q5_control)
total.control[[length(total.control)]]

total.pooled<-addmargins(table_pooled_Q5)
total.pooled[[length(total.pooled)]]

total<-cbind(total.uas[[length(total.uas)]], total.pooled[[length(total.pooled)]], total.control[[length(total.control)]])
total
```


```{r, include = FALSE}
table_Q5_pcw <- cbind(table_cr030_w, table_pooled_Q5, table_Q5_control)
print(table_Q5_pcw)
prop.table(table_Q5_pcw, 2)
chisq.test(table_Q5_pcw)
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q5_pcw, 2)*100, format = "f" , digits = 1), formatC(total, format = "d"))
rownames(table) <- c("Very Unlikely", "Somewhat Unlikely", "Somewhat Likely", "Very Likely", "Unsure" ,"Total N")
colnames(table) <- c("UAS Only (%)", "All Other Images (%)",  "Neutral Image (%)")
table
```

```{r, echo = FALSE}
require(knitr)

kable(table, 
            caption = "Table 5. Comparing responses from Understanding America Survey, Facebook Advertisement Pooled Images, and Control Image Only for \"How likely are you to get vaccinated for coronavirus once a vaccine is available to the public?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote("Note: Proportion of respondents for each category; X-squared = 284.5, df = 8, p < 0.001", notation = "none") %>%
  row_spec(6, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```
```{r, include = FALSE}
table_pooled_Q6 <-table(pooled.data$Q6)
table_pooled_Q6
prop.table(table_pooled_Q6)
```

```{r, include = FALSE}
table_Q6_control <-table(control.data$Q6)
table_Q6_control
prop.table(table_Q6_control)
```
```{r, include = FALSE}
total.uas<-addmargins(table_cr018a_w)
total.uas[[length(total.uas)]]

total.control<-addmargins(table_Q6_control)
total.control[[length(total.control)]]

total.pooled<-addmargins(table_pooled_Q6)
total.pooled[[length(total.pooled)]]

total<-cbind(total.uas[[length(total.uas)]], total.pooled[[length(total.pooled)]], total.control[[length(total.control)]])
total
```
```{r, include = FALSE}
table_Q6_pcw <- cbind(table_cr018a_w, table_Q6_control, table_pooled_Q6)
print(table_Q6_pcw)
prop.table(table_Q6_pcw, 2)
chisq.test(table_Q6_pcw)
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q6_pcw, 2)*100, format = "f" , digits = 1), formatC(total, format = "d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("UAS Only (%)", "All Other Images (%)",  "Neutral Image (%)")
table
```

```{r, echo = FALSE}
require(knitr)

kable(table, 
            caption = "Table 6. Comparing responses from Understanding America Survey, Facebook Advertisement Pooled Images, and Control Image Only for \"Are Federal, state, or local governments currently requiring you to limit non-essential travel?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote("Note: Proportion of respondents for each category; X-squared = 66.4, df = 4, p < 0.001", notation = "none") %>%
  row_spec(4, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```
### FINANCE
Table 7. The first finance question is on a 0-100 scale. 

```{r, include = FALSE}
table_pooled_Q8 <-table(pooled.data$Q8)
table_pooled_Q8
prop.table(table_pooled_Q8)
```
```{r, include = FALSE}
table_Q8_control <-table(control.data$Q8)
table_Q8_control
prop.table(table_Q8_control)
```
```{r, include = FALSE}
total.uas<-addmargins(table_ei002_w)
total.uas[[length(total.uas)]]

total.control<-addmargins(table_Q8_control)
total.control[[length(total.control)]]

total.pooled<-addmargins(table_pooled_Q8)
total.pooled[[length(total.pooled)]]

total<-cbind(total.uas[[length(total.uas)]], total.pooled[[length(total.pooled)]], total.control[[length(total.control)]])
total
```
```{r, include = FALSE}
table_Q8_pcw <- cbind(table_ei002_w, table_pooled_Q8, table_Q8_control)
print(table_Q8_pcw)
prop.table(table_Q8_pcw, 2)
chisq.test(table_Q8_pcw)
```
```{r, include = FALSE}
options(kableExtra.latex.load_packages = FALSE)
table<-rbind(formatC(prop.table(table_Q8_pcw, 2)*100, format = "f" , digits = 1), formatC(total, format = "d"))
rownames(table) <- c("Yes", "No", "Unsure", "Total N")
colnames(table) <- c("UAS Only (%)", "All Other Images (%)",  "Neutral Image (%)")
table
```

```{r, echo = FALSE}
require(knitr)

kable(table, 
  caption = "Table 8. Comparing responses from Understanding America Survey, Facebook Advertisement Pooled Images, and Control Image Only for \"In the past seven days, were you worried you would run out of food because of a lack of money or other resources?\"", 
            digits = 2,
            align = "c") %>%
  add_footnote("Note: Proportion of respondents for each category; X-squared = 14.8, df = 4, p = 0.005", notation = "none") %>%
  row_spec(4, bold = TRUE) %>%
  kable_styling(latex_options = c("striped", full_width = F, "hold_position"))
```

